Supplement B: Stationwise Evaluation

### 2018-11-04 pkg/disttree/inst/draft/draft.Rnw
final formatting
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2378 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 4503d2d73b067eabaa07a9184943d75e94a802fc

\section*{Appendix}
\begin{appendix}

@@

\subsection*{Supplement B: Stationwise Evaluation}
  To show that Axams is a fairly typical
  station and similar insights can be obtained for other stations as well,
  this supplement presents the same analysis as in Section~3.3 of the main
  manuscript for 14~further meteorological stations.

\bibliography{ref.bib}

>>>>

\newpage
\section*{Appendix}
\begin{appendix}

@@

\subsection*{Supplement B: Stationwise Evaluation}
  To show that Axams is a fairly typical
  station and similar insights can be obtained for other stations as well,
  this supplement presents the same analysis as in Section~\ref{sec:axams} of the main
  manuscript for 14~further meteorological stations.

\newpage
\bibliography{ref.bib}

### 2018-11-04 pkg/disttree/inst/draft/rejoinder.Rnw
removed highlighting of changed/revised parts; typos
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2376 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 16004c6499fa53e2d5192a1c5cfc9f6db6a312de
final formatting
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2378 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 4503d2d73b067eabaa07a9184943d75e94a802fc

\item \emph{Supplement A: Different response distributions.}\\
To assess the appropriateness and robustness of the distributional
assumption (censored Gaussian) made in the main manuscript, further
response distributions (two-part Gaussian hurdle; censored
logistic) are evaluated to potentially better capture lower
and upper tails, respectively. The supplement follows the
evaluations performed for all 95 observation stations 
in the main manuscript using all three response distributions
for a subset of 15 stations.

\item \emph{Supplement B: Stationwise evaluation.}\\
To show that the more extensive cross-validation results -- obtained only
for one station (Axams) in the main manuscript -- are fairly typical,
they are extended to 14 other observation stations. This also incorporates
results that were previously presented in Appendix B which has consequently
been omitted from the main manuscript.

@@

\vspace*{-2.8cm}
\hspace*{-0.3cm} 
%\includegraphics[width = 0.23\textwidth]{signature-Schlosser}

>>>>

\item \emph{Supplement A: Different Response Distributions.}\\
To assess the appropriateness and robustness of the distributional
assumption (censored Gaussian) made in the main manuscript, further
response distributions (two-part Gaussian hurdle; censored
logistic) are evaluated to potentially better capture lower
and upper tails, respectively. The supplement follows the
evaluations performed for all 95 observation stations 
in the main manuscript using all three response distributions
for a subset of 15 stations.

\item \emph{Supplement B: Stationwise Evaluation.}\\
To show that the more extensive cross-validation results -- obtained only
for one station (Axams) in the main manuscript -- are fairly typical,
they are extended to 14 other observation stations. This also incorporates
results that were previously presented in Appendix B which has consequently
been omitted from the main manuscript.

@@

\vspace*{-2.8cm}
\hspace*{-0.3cm} 
\includegraphics[width = 0.23\textwidth]{signature-Schlosser}

### 2018-11-04 pkg/disttree/inst/draft/supplement/Rain_stationwise_results.Rnw
changed numbering of supplements (A and B instead of 1 and 2)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2369 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 9093ae989a286d620c85bcfcb92b68ad87d3c504
final formatting
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2378 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 4503d2d73b067eabaa07a9184943d75e94a802fc

<<pit, fig=TRUE, echo=FALSE, height=6, width = 7>>=
set.seed(4)
par(mfrow = c(2, 2))
pithist(results$pit_df, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Distributional forest", ylim = c(0, 1.9))
pithist(results$pit_ml, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "EMOS", ylim = c(0, 1.9))
if(!all(is.na(results$pit_g))) pithist(results$pit_g,  nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Prespecified GAMLSS", ylim = c(0, 1.9))
pithist(results$pit_gb, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "boosted GAMLSS", ylim = c(0, 1.9))
@

>>>>

<<pit, fig=TRUE, echo=FALSE, height=6, width = 7>>=
set.seed(4)
par(mfrow = c(2, 2))
pithist(results$pit_df, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Distributional forest", ylim = c(0, 1.9))
pithist(results$pit_ml, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "EMOS", ylim = c(0, 1.9))
if(!all(is.na(results$pit_g))) pithist(results$pit_g,  nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Prespecified GAMLSS", ylim = c(0, 1.9))
pithist(results$pit_gb, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Boosted GAMLSS", ylim = c(0, 1.9))
@
